RIScatter: Unifying\\Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface

### 2022-10-13 assets/illustration/ambc.tex
:paintbrush: Update illustrations

	\draw[decorate,decoration={waves,segment length=5mm}] (1,-0.5) -- (7.5,-0.5);
	\draw[decorate,decoration={waves,segment length=5mm}] (0.25,1) -- (0.75,3);
	\draw[decorate,decoration={waves,segment length=5mm}] (0.75,0.25) -- (5.5,2.5);
	\draw[decorate,decoration={triangles,segment length=2.5mm}] (5.5,3.5) -- (2.5,3.5);
	\draw[decorate,decoration={triangles,segment length=2.5mm}] (7.5,3) -- (8,1);

	\node[draw=none] at (4,0.35) {Modulated\\Signal};
	\node[draw=none] at (4,3.5) {Superimposed\\Signal};
\end{tikzpicture}

>>>>

	\draw[decorate,decoration={waves,segment length=5mm}] (1,-0.5) -- (7.5,-0.5);
	\draw[decorate,decoration={waves,segment length=5mm}] (0.25,1) -- (0.75,3);
	\draw[decorate,decoration={waves,segment length=5mm}] (0.75,0.25) -- (5.5,2.5);
	\draw[decorate,decoration={triangles,segment length=5mm,shape size=1.5mm}] (5.5,3.5) -- (2.5,3.5);
	\draw[decorate,decoration={triangles,segment length=5mm,shape size=1.5mm}] (7.5,3) -- (8,1);

	\node[draw=none] at (4,0.35) {Modulated\\Signal};
	\node[draw=none] at (4,3.95) {Superimposed};
	\node[draw=none] at (4,3) {Signal};
\end{tikzpicture}

### 2022-10-13 assets/illustration/bbc.tex
:paintbrush: Update illustrations

\begin{tikzpicture}[font=\LARGE,every node/.style={draw,ultra thick},every path/.style={ultra thick},every text node part/.style={align=center}]
	\node at (0,0) [isosceles triangle,isosceles triangle stretches,shape border rotate=+90,minimum size=1cm,minimum height=1cm,anchor=north] {};
	\node at (5,3) [rectangle,minimum size=1cm] {};
	\node at (8,0) [isosceles triangle,isosceles triangle stretches,shape border rotate=+270,minimum size=1cm,minimum height=1cm,anchor=north] {};

	\node[draw=none] at (0,-2) {Carrier\\Emitter};
	\node[draw=none] at (5,4.5) {Scattering\\Node};
	\node[draw=none] at (8,-2) {Backscatter\\Reader};

	\draw[decorate,decoration={snake,post length=2.5mm},-latex] (1,-1) -- (7.5,-1);
	\draw[decorate,decoration={snake,post length=2.5mm},-latex] (0.5,0) -- (4,3);
	\draw[decorate,decoration={snake,pre length=1cm,post length=1cm},-latex] (6,3) -- (8,0.35);

	\node[draw=none] at (1.5,2.2) {Carrier};
	\node[draw=none] at (7.25,2.2) {1};
	\node[draw=none] at (6.55,3.1) {0};
	\node[draw=none] at (7.95,1.3) {0};
\end{tikzpicture}

>>>>

\begin{tikzpicture}[font=\LARGE,every node/.style={draw,ultra thick},every path/.style={ultra thick},every text node part/.style={align=center}]
	\node at (0,0) [isosceles triangle,isosceles triangle stretches,shape border rotate=+90,minimum size=1cm,minimum height=1cm,anchor=north] {};
	\node at (5,2) [rectangle,minimum size=1cm] {};
	\node at (8,0) [isosceles triangle,isosceles triangle stretches,shape border rotate=+270,minimum size=1cm,minimum height=1cm,anchor=north] {};

	\node[draw=none] at (0,-1.95) {Carrier\\Emitter};
	\node[draw=none] at (5,3.35) {Scattering\\Node};
	\node[draw=none] at (8,-1.95) {Backscatter\\Reader};

	\draw[decorate,decoration={snake,post length=2.5mm},-latex] (1,-1) -- (7.5,-1);
	\draw[decorate,decoration={snake,post length=2.5mm},-latex] (0.5,0) -- (4,2);
	\draw[decorate,decoration={snake,pre length=7.5mm,post length=7.5mm},-latex] (6,2) -- (8,0.35);

	\node[draw=none] at (1.5,1.75) {Carrier};
	\node[draw=none] at (7.2,1.7) {1};
	\node[draw=none] at (6.6,2.25) {0};
	\node[draw=none] at (7.8,1.15) {0};
\end{tikzpicture}

### 2022-10-13 assets/illustration/discrete_outputs.tex
:paintbrush: Update illustrations

\begin{tikzpicture}
	\begin{axis}[width=8cm,height=4cm,xmin=0,xmax=6.5,xlabel=$z$,axis x line=middle,axis y line=none,xtick={0,2,3,4,6},xticklabels={$t_0$,$t_1$,$t_2$,$t_3$,$t_4$},xtick style={draw=none},every axis x label/.style={at=(current axis.right of origin),anchor=west},domain=0:6]
		\addplot[mark=*,mark size=1pt,only marks,color=gray] {0};
		\addplot[mark=*,mark size=1pt,only marks,color=black] coordinates{(0,0) (2,0) (3,0) (4,0) (6,0)};
		\draw[color=black,dashed] (0,0) -- (0,0.6);
		\draw[color=black,dashed] (2,0) -- (2,0.6);
		\draw[color=black,dashed] (3,0) -- (3,0.6);
		\draw[color=black,dashed] (4,0) -- (4,0.6);
		\draw[color=black,dashed] (6,0) -- (6,0.6);
		\draw[latex-latex] (0,0.6) -- (2,0.6) node[below,midway]{$\mathcal{R}_1$};
		\draw[latex-latex] (2,0.6) -- (3,0.6) node[below,midway]{$\mathcal{R}_2$};
		\draw[latex-latex] (3,0.6) -- (4,0.6) node[below,midway]{$\mathcal{R}_3$};
		\draw[latex-latex] (4,0.6) -- (6,0.6) node[below,midway]{$\mathcal{R}_4$};
	\end{axis}
\end{tikzpicture}

>>>>

\begin{tikzpicture}
	\begin{axis}[width=10cm,height=5cm,xmin=0,xmax=6.5,xlabel=$z$,axis x line=middle,axis y line=none,xtick={0,2,3,4,6},xticklabels={$t_0$,$t_1$,$t_2$,$t_3$,$t_4$},xtick style={draw=none},every axis x label/.style={at=(current axis.right of origin),anchor=west},domain=0:6]
		\addplot[mark=*,mark size=0.5pt,only marks,color=gray] {0};
		\addplot[mark=*,mark size=1pt,only marks,color=black] coordinates{(0,0) (2,0) (3,0) (4,0) (6,0)};
		\draw[decorate,decoration={brace,amplitude=10}] (0,0) -- (2,0) node[above,midway,yshift=10]{$\mathcal{R}_1$};
		\draw[decorate,decoration={brace,amplitude=10}] (2,0) -- (3,0) node[above,midway,yshift=10]{$\mathcal{R}_2$};
		\draw[decorate,decoration={brace,amplitude=10}] (3,0) -- (4,0) node[above,midway,yshift=10]{$\mathcal{R}_3$};
		\draw[decorate,decoration={brace,amplitude=10}] (4,0) -- (6,0) node[above,midway,yshift=10]{$\mathcal{R}_4$};
	\end{axis}
\end{tikzpicture}

### 2022-10-13 assets/illustration/energy_distribution.tex
:paintbrush: Update illustrations

\begin{tikzpicture}
	\begin{axis}[
			height=5cm,
			width=9cm,
			xlabel = $z$,
			ylabel = {Probability Density},
			font=\scriptsize,
			no markers,
			xmin=0,
			ymin=0,
			xmax=70,
			xtick={0,12.78,20.28,29.62,70},
			xticklabels={$t_0$,$t_1$,$t_2$,$t_3$,$t_4$},
			yticklabels={},
			samples = 200
		]

		\addplot+[thick] gnuplot[raw gnuplot] {%
				isint(x) = (int(x)==x);
				gmm(x,rho,lambda)=rho<=0||lambda<=0?1/0:  x<0?0.0:x==0?(rho>1?0.0:rho==1?real(lambda):1/0):  exp(rho*log(lambda)+(rho-1.0)*log(x)-lgamma(rho)-lambda*x);
				set xrange [0:80];
				set yrange [0:1];
				samples=200;
				plot gmm(x,10,1)};
		\addlegendentryexpanded{$f(z \mid \mathcal{H}_1)$}

		\addplot+[thick] gnuplot[raw gnuplot] {%
				isint(x) = (int(x)==x);
				gmm(x,rho,lambda)=rho<=0||lambda<=0?1/0:  x<0?0.0:x==0?(rho>1?0.0:rho==1?real(lambda):1/0):  exp(rho*log(lambda)+(rho-1.0)*log(x)-lgamma(rho)-lambda*x);
				set xrange [0:80];
				set yrange [0:1];
				samples=200;
				plot gmm(x,10,0.6)};
		\addlegendentryexpanded{$f(z \mid \mathcal{H}_2)$}

		\addplot+[thick,color=brown] gnuplot[raw gnuplot] {%
				isint(x) = (int(x)==x);
				gmm(x,rho,lambda)=rho<=0||lambda<=0?1/0:  x<0?0.0:x==0?(rho>1?0.0:rho==1?real(lambda):1/0):  exp(rho*log(lambda)+(rho-1.0)*log(x)-lgamma(rho)-lambda*x);
				set xrange [0:80];
				set yrange [0:1];
				samples=200;
				plot gmm(x,10,0.4)};
		\addlegendentryexpanded{$f(z \mid \mathcal{H}_3)$}

		\addplot+[thick,color=green!40!gray] gnuplot[raw gnuplot] {%
				isint(x) = (int(x)==x);
				gmm(x,rho,lambda)=rho<=0||lambda<=0?1/0:  x<0?0.0:x==0?(rho>1?0.0:rho==1?real(lambda):1/0):  exp(rho*log(lambda)+(rho-1.0)*log(x)-lgamma(rho)-lambda*x);
				set xrange [0:80];
				set yrange [0:1];
				samples=200;
				plot gmm(x,10,0.28)};
		\addlegendentryexpanded{$f(z \mid \mathcal{H}_4)$}
		\draw[color=gray,thick,dashed] (12.78,0) -- (12.78,0.1);
		\draw[color=gray,thick,dashed] (20.28,0) -- (20.28,0.1);
		\draw[color=gray,thick,dashed] (29.62,0) -- (29.62,0.1);
		\draw[latex-latex] (0,0.05) -- (12.78,0.05) node[below,midway]{$\mathcal{R}_1$};
		\draw[latex-latex] (12.78,0.05) -- (20.28,0.05) node[below,midway]{$\mathcal{R}_2$};
		\draw[latex-latex] (20.28,0.05) -- (29.62,0.05) node[below,midway]{$\mathcal{R}_3$};
		\draw[latex-latex] (29.62,0.05) -- (70,0.05) node[below,midway]{$\mathcal{R}_4$};
	\end{axis}
\end{tikzpicture}

>>>>

\definecolor{color1}{HTML}{0072BD}
\definecolor{color2}{HTML}{D95319}
\definecolor{color3}{HTML}{EDB120}
\definecolor{color4}{HTML}{7E2F8E}

\begin{tikzpicture}
	\begin{axis}[
			clip mode=individual,
			height=5cm,
			width=9cm,
			xlabel = $z$,
			ylabel = {Probability Density},
			font=\scriptsize,
			no markers,
			xmin=0,
			ymin=0,
			xmax=70,
			xtick={0,12.78,20.28,29.62,70},
			xticklabels={$t_0$,$t_1$,$t_2$,$t_3$,$t_4$},
			yticklabels=\empty,
			samples = 200
		]

		\addplot+[very thick,solid,color1] gnuplot[raw gnuplot] {%
				isint(x) = (int(x)==x);
				gmm(x,rho,lambda)=rho<=0||lambda<=0?1/0:  x<0?0.0:x==0?(rho>1?0.0:rho==1?real(lambda):1/0):  exp(rho*log(lambda)+(rho-1.0)*log(x)-lgamma(rho)-lambda*x);
				set xrange [0:80];
				set yrange [0:1];
				samples=200;
				plot gmm(x,10,1)};
		\addlegendentryexpanded{$f(z \mid \mathcal{H}_1)$}

		\addplot+[very thick,dashed,color2] gnuplot[raw gnuplot] {%
				isint(x) = (int(x)==x);
				gmm(x,rho,lambda)=rho<=0||lambda<=0?1/0:  x<0?0.0:x==0?(rho>1?0.0:rho==1?real(lambda):1/0):  exp(rho*log(lambda)+(rho-1.0)*log(x)-lgamma(rho)-lambda*x);
				set xrange [0:80];
				set yrange [0:1];
				samples=200;
				plot gmm(x,10,0.6)};
		\addlegendentryexpanded{$f(z \mid \mathcal{H}_2)$}

		\addplot+[very thick,dotted,color3] gnuplot[raw gnuplot] {%
				isint(x) = (int(x)==x);
				gmm(x,rho,lambda)=rho<=0||lambda<=0?1/0:  x<0?0.0:x==0?(rho>1?0.0:rho==1?real(lambda):1/0):  exp(rho*log(lambda)+(rho-1.0)*log(x)-lgamma(rho)-lambda*x);
				set xrange [0:80];
				set yrange [0:1];
				samples=200;
				plot gmm(x,10,0.4)};
		\addlegendentryexpanded{$f(z \mid \mathcal{H}_3)$}

		\addplot+[very thick,dashdotted,color4] gnuplot[raw gnuplot] {%
				isint(x) = (int(x)==x);
				gmm(x,rho,lambda)=rho<=0||lambda<=0?1/0:  x<0?0.0:x==0?(rho>1?0.0:rho==1?real(lambda):1/0):  exp(rho*log(lambda)+(rho-1.0)*log(x)-lgamma(rho)-lambda*x);
				set xrange [0:80];
				set yrange [0:1];
				samples=200;
				plot gmm(x,10,0.28)};
		\addlegendentryexpanded{$f(z \mid \mathcal{H}_4)$}
		\draw[latex-latex] (0,0) -- (12.78,0) node[above,midway,yshift=-2]{$\mathcal{R}_1$};
		\draw[latex-latex] (12.78,0) -- (20.28,0) node[above,midway,yshift=-2]{$\mathcal{R}_2$};
		\draw[latex-latex] (20.28,0) -- (29.62,0) node[above,midway,yshift=-2]{$\mathcal{R}_3$};
		\draw[latex-latex] (29.62,0) -- (70,0) node[above,midway,yshift=-2]{$\mathcal{R}_4$};
	\end{axis}
\end{tikzpicture}

### 2022-10-13 assets/illustration/ris.tex
:paintbrush: Update illustrations

\begin{tikzpicture}[font=\LARGE,every node/.style={draw,ultra thick},every path/.style={ultra thick},every text node part/.style={align=center}]
	\node at (0,0) [circular sector,shape border rotate=90,minimum width=2cm] {};
	\node at (5,3) [rectangle,minimum size=1cm] {};
	\node at (8,0.55) [circular sector,shape border rotate=270,minimum width=2cm] {};

	\node[draw=none] at (0,-1.25) {Primary\\Transmitter};
	\node[draw=none] at (5,4.375) {Scattering\\Node};
	\node[draw=none] at (8,-1.25) {Cooperative\\Receiver};

	\draw[decorate,decoration={waves,segment length=5mm}] (1,-0.25) -- (7.375,-0.25);
	\draw[decorate,decoration={waves,segment length=5mm}] (0.5,0.75) -- (4,3);
	\draw[decorate,decoration={triangles,segment length=2.5mm}] (6,3) -- (8,1.25);

	\node[draw=none] at (4,0.875) {Modulated\\Signal};
	\node[draw=none] at (7.8,2.9) {Superimposed\\Signal};
\end{tikzpicture}

>>>>

\begin{tikzpicture}[font=\LARGE,every node/.style={draw,ultra thick},every path/.style={ultra thick},every text node part/.style={align=center}]
	\node at (0,0) [dart,shape border rotate=90,minimum width=1cm] {};
	\node at (5,3.25) [semicircle,shape border rotate=180,minimum width=1.5cm] {};
	\node at (8,0.35) [dart,shape border rotate=270,minimum width=1cm] {};

	\node[draw=none] at (0,-1) {Transmitter};
	\node[draw=none] at (5,4.4375) {Reflecting\\Element};
	\node[draw=none] at (8,-1) {Receiver};

	\draw[decorate,decoration={waves,segment length=5mm}] (1,-0.25) -- (7.375,-0.25);
	\draw[decorate,decoration={waves,segment length=5mm}] (0.5,0.75) -- (4,3);
	\draw[decorate,decoration={waves,segment length=5mm}] (6,3) -- (8,1.25);

	\node[draw=none] at (4.875,1.125) {Modulated\\Signal};
\end{tikzpicture}

### 2022-10-13 main.tex
:paintbrush: Update illustrations

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bookmark}
\usepackage{booktabs}
\usepackage[american]{circuitikz}
\usepackage{cite}
\usepackage{fixmath}
\usepackage[acronym]{glossaries-extra}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage[short]{optidef}
\usepackage{pgfplots}
\usepackage[subtle]{savetrees}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage{tabularx}
\usepackage{tikz}
\usepackage{xcolor}

% dark mode
\usepackage{xcolor} \pagecolor[rgb]{0,0,0} \color[rgb]{1,1,1}

@@

		The backscatter reader can be either co-located or separated with the carrier emitter, known as \gls{mbc} and \gls{bbc} in Fig. \subref*{fi:monostatic_backscatter_communication} and \subref*{fi:bistatic_backscatter_communication}, respectively.

@@

		As illustrated in Fig. \subref*{fi:ambient_backscatter_communication}, it eliminates the need of dedicated power supply, carrier emitter and frequency spectrum, bringing more opportunities to low-power communications.

@@

		The concept of cooperative \gls{ambc} was further refined as \gls{sr} in Fig. \subref*{fi:symbiotic_radio} that cognitively incorporates \gls{ambc} with existing systems \cite{Liang2020}.

@@

		On the other hand, \gls{ris} in Fig. \subref*{fi:reconfigurable_intelligent_surface} is a promising technology that evolves wireless propagation environment using numerous passive reflecting elements (e.g., scattering antenna or programmable metamaterial) with adjustable amplitudes and/or phases \cite{Wu2021b}.

@@

		\begin{figure}[!t]
			\centering
			\subfloat[\gls{mbc}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/monostatic_backscatter_communication.tex}
				}
				\label{fi:monostatic_backscatter_communication}
			}
			\subfloat[\gls{bbc}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/bistatic_backscatter_communication.tex}
				}
				\label{fi:bistatic_backscatter_communication}
			}
			\\
			\subfloat[\gls{ambc}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/ambient_backscatter_communication.tex}
				}
				\label{fi:ambient_backscatter_communication}
			}
			\subfloat[\gls{sr}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/symbiotic_radio.tex}
				}
				\label{fi:symbiotic_radio}
			}
			\\
			\subfloat[\gls{ris}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/reconfigurable_intelligent_surface.tex}
				}
				\label{fi:reconfigurable_intelligent_surface}
			}
			\subfloat[RIScatter]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/riscatter.tex}
				}
				\label{fi:riscatter}
			}
			\caption{
				Illustration of scattering applications.
				% Paradigms for various scattering applications.
			}
			\label{fi:scatter_comparison}
		\end{figure}
	\end{subsection}

	\begin{table*}[]
		\caption{Comparison of Scattering Applications}
		\begin{tabularx}{\textwidth}{XXXXXXX}
			\toprule
			                              & \gls{mbc}               & \gls{bbc}               & \gls{ambc}                                      & \gls{sr}                                     & \gls{ris}                       & RIScatter                                         \\ \midrule
			Coexisting systems            & 1                       & 1                       & 2 (competitive)                                 & 2 (collaborative)                            & 1                               & 2 (collaborative)                                 \\ \midrule
			Scatterer contribution        & Backscatter modulation  & Backscatter modulation  & Backscatter modulation and primary interference & Backscatter modulation and primary multipath & Passive beamforming             & Backscatter modulation and passive beamforming    \\ \midrule
			Cooperative transmission      & ---                     & ---                     & No                                              & Active beamforming                           & ---                             & Active beamforming and smart reflection           \\ \midrule
			Cooperative reception         & ---                     & ---                     & No                                              & Joint detection or \gls{sic}                 & ---                             & Backscatter detection as primary channel training \\ \midrule
			Backscatter detection         & Coherent or noncoherent & Coherent or noncoherent & Semi-coherent or noncoherent                    & Coherent                                     & ---                             & Semi-coherent                                     \\ \midrule
			Reflection state distribution & Equiprobable            & Equiprobable            & Equiprobable                                    & Gaussian or Equiprobable                     & Degenerate (\gls{csi}-adaptive) & Flexible (\gls{csi}- and link priority-adaptive)  \\ \midrule
			Load-switching frequency      & Fast or slow            & Fast or slow            & Fast or slow                                    & Slow                                         & Slow (dynamic) or very slow     & Fast or slow                                      \\ \bottomrule
		\end{tabularx}
	\end{table*}

>>>>

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bookmark}
\usepackage{booktabs}
\usepackage[american]{circuitikz}
\usepackage{cite}
\usepackage{fixmath}
\usepackage[acronym]{glossaries-extra}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage[short]{optidef}
\usepackage{pgfplots}
\usepackage{ragged2e}
\usepackage[subtle]{savetrees}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage{tabularx}
\usepackage{tikz}
\usepackage{xcolor}

% dark mode
% \usepackage{xcolor} \pagecolor[rgb]{0,0,0} \color[rgb]{1,1,1}

@@

		The backscatter reader can be either co-located or separated with the carrier emitter, known as \gls{mbc} and \gls{bbc} in Fig. \subref*{fi:mbc} and \subref*{fi:bbc}, respectively.

@@

		As illustrated in Fig. \subref*{fi:ambc}, it eliminates the need of dedicated power supply, carrier emitter and frequency spectrum, bringing more opportunities to low-power communications.

@@

		The concept of cooperative \gls{ambc} was further refined as \gls{sr} in Fig. \subref*{fi:sr} that cognitively incorporates \gls{ambc} with existing systems \cite{Liang2020}.

@@

		On the other hand, \gls{ris} in Fig. \subref*{fi:ris} is a promising technology that evolves wireless propagation environment using numerous passive reflecting elements (e.g., scattering antenna or programmable metamaterial) with adjustable amplitudes and/or phases \cite{Wu2021b}.

@@

		\begin{figure}[!t]
			\centering
			\subfloat[\gls{mbc}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/mbc.tex}
				}
				\label{fi:mbc}
			}
			\subfloat[\gls{bbc}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/bbc.tex}
				}
				\label{fi:bbc}
			}
			\\
			\subfloat[\gls{ambc}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/ambc.tex}
				}
				\label{fi:ambc}
			}
			\subfloat[\gls{sr}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/sr.tex}
				}
				\label{fi:sr}
			}
			\\
			\subfloat[\gls{ris}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/ris.tex}
				}
				\label{fi:ris}
			}
			\subfloat[RIScatter]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/riscatter.tex}
				}
				\label{fi:riscatter}
			}
			\caption{
				Illustration of scattering applications.
				% Paradigms for various scattering applications.
			}
			\label{fi:scatter_comparison}
		\end{figure}
	\end{subsection}

	\begin{table*}[]
		\caption{Comparison of Scattering Applications}
		\begin{tabularx}{\textwidth}{CCCCCCC}
			\toprule
			                              & \gls{mbc}                 & \gls{bbc}                 & \gls{ambc}                                      & \gls{sr}                                     & \gls{ris}                               & RIScatter                                         \\ \midrule
			Coexisting systems            & 1                         & 1                         & 2 (competitive)                                 & 2 (collaborative)                            & 1                                       & 2 (collaborative)                                 \\ \midrule
			Scatterer contribution        & Backscatter modulation    & Backscatter modulation    & Backscatter modulation and primary interference & Backscatter modulation and primary multipath & Passive beamforming                     & Backscatter modulation and passive beamforming    \\ \midrule
			Cooperative transmission      & ---                       & ---                       & No                                              & Active beamforming                           & ---                                     & Active beamforming and smart reflection           \\ \midrule
			Cooperative reception         & ---                       & ---                       & No (separated receivers)                        & Joint detection or \gls{sic}                 & ---                                     & Backscatter detection as primary channel training \\ \midrule
			Primary detection             & ---                       & ---                       & Semi-coherent                                   & Coherent or semi-coherent                    & Coherent                                & Coherent                                          \\ \midrule
			Backscatter detection         & Coherent                  & Coherent                  & Semi-coherent or noncoherent                    & Coherent                                     & ---                                     & Semi-coherent                                     \\ \midrule
			Reflection state distribution & Equiprobable (line-coded) & Equiprobable (line-coded) & Equiprobable (line-coded)                       & Equiprobable or Gaussian                     & Degenerate (\gls{csi}-adaptive)         & Flexible (\gls{csi}- and link priority-adaptive)  \\ \midrule
			Load-switching frequency      & Fast or slow              & Fast or slow              & Fast or slow                                    & Slow                                         & Slow (dynamic) or very slow (blockwise) & Fast or slow                                      \\ \bottomrule
		\end{tabularx}
	\end{table*}
